\documentclass[addpoints,12pt]{exam}

\usepackage{amsmath}

\begin{document}
\title{DATA 335 - Winter 2026 - Quiz 1}
\date{February 11, 2026}
\maketitle

\makebox[\textwidth]{Name:\enspace\hrulefill}

\vspace{1cm}

\makebox[\textwidth]{Student ID:\enspace\hrulefill}

\vspace{1cm}

\begin{center}
\gradetable[v][questions]
\end{center}

\vspace{1cm}
\section*{Instructions}

\begin{itemize}
    \item Complete all four problems in this booklet.
    
    \item Justify your answers fully, transcribing Python code where appropriate.
    
    \item You may use a computer to run Python code, search package documentation, and refer to any relevant course materials (Jupyter notebooks, textbooks, etc.).
    
    \item Use of AI chatbots/agents is prohibited.
    
    \item The time limit is 50 minutes.
\end{itemize}

\newpage
\begin{questions}

    \question
    Each bag in a large box contains $25$ tulip bulbs.
    It is known that $60\%$ of the bags contain bulbs for $5$ red and $20$ yellow tulips, while the remaining $40\%$ of the bags contain bulbs for $15$ red and $10$ yellow tulips.
    A bag is selected at random and a bulb taken at random from this bag is planted.

    \begin{parts}
    \part[2] What is the probability that a yellow tulip will grow?
    \vspace{8cm}
    \part[2] Given that the tulip is yellow, what is the probability that it came from a bag containing $5$ red and $20$ yellow bulbs?
    \end{parts}

    \newpage
    \question[3] On average, a grocer sells three of a certain article per week.
    What is the smallest number these articles that the grocer must have in stock so that the chance of running out within a week is less than $0.01$?
    Assume a Poisson distribution.

    \newpage
    \question Let random variable $\theta$ represent the rate at which people receive text messages, measured in messages per hour.
    At first, you believe that the typical number of messages per hour is $5$ with a standard deviation of $0.25$.

    \begin{parts}
        \part[2] Tune an appropriate $\operatorname{Gamma}(s,r)$ prior model for $\theta$.
        \vspace{8cm}
        \part[2] What is the prior probability that the rate of text messages per hour is larger than $10$?
    \end{parts}

    \newpage
    \question In a study of water quality, $n = 176$ samples were taken from streams having a high environmental impact from sheep farming.
    Of these, $y = 44$ had a high Campylobacter (a kind of bacteria) level.
    Let $\theta$ be the probability that a sample of water from this type of stream has a high Campylobacter level.

    \begin{parts}
    \part[2] Using a $\operatorname{Beta}(1,10)$, calculate the posterior distribution for $\theta$.

    \vspace{8cm}
    \part[2] Perform a Bayesian hypothesis test of
    $$
    H_0: \theta\leq 0.15\qquad\text{versus}\qquad H_1: \theta > 0.15
    $$
    at the $0.05$ level of significance.
    \end{parts}

    \newpage
    \noindent Extra sheet
\end{questions}




\end{document}